Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-06-28 analysis/paper/paper.Rnw
updated paper methods section

For each hotspot, we paired each local trait with each nonlocal trait and performed a
two-dimensional, two-QTL scan over a genomic region that included the entirety of the
hotspot. We fitted bivariate linear mixed effects models at each ordered pair of markers in a two-dimensional grid \citep{boehm2019testing}.

@@

From the two-dimensional scans, we calculated pleiotropy likelihood ratio test statistics for each
pair of traits \citep{jiang1995multiple,boehm2019testing, boehm2019thesis}. Because of the required
computing time for bootstrap analyses, we didn't obtain p-values for the pleiotropy tests. Instead,
we worked directly with the test statistic values.

>>>>

For each hotspot, we tested all pairs of traits, regardless of whether the traits were local or nonlocal. We performed a
two-dimensional, two-QTL scan over a genomic region that included the entirety of the
hotspot. We fitted bivariate linear mixed effects models at each ordered pair of markers in a two-dimensional grid \citep{boehm2019testing}.

@@

\begin{equation}
G \sim MN_{n x 2}(0, K, V_g)
\end{equation}

\begin{equation}
E \sim MN_{n x 2}(0, I_n, V_e)
\end{equation}

and $G$ and $E$ are independent.

\begin{equation}
\hat B = (X^T\hat \Sigma^{-1}X)^{-1}X^T\hat\Sigma^{-1}Y
\label{eq:Bhat}
\end{equation}

\begin{equation}
\hat \Sigma = \hat V_g \otimes \hat K + \hat V_e \otimes I_n
\label{eq:Sigmahat}
\end{equation}

\begin{equation}
l_{10}(\hat B, \hat \Sigma) = - \frac{1}{2}\log_{10}\left((Y - X\hat B)^T\hat \Sigma^{-1}(Y - X\hat B)\right) - n\log_{10}(2\pi) - \log_{10}|\hat \Sigma|
\label{eq:loglik}
\end{equation}

For $n$ mice, $\Sigma$ is a $2n$ by $2n$ covariance matrix, while $V_g$ and $V_e$ are $2$ by $2$ covariance matrices. Estimates $\hat V_g$ and $\hat V_e$ are obtained via an expectation-maximization algorithm \citep{zhou2014efficient,gemma2}

\subsubsection{Calculating likelihood ratio test statistics}
From the two-dimensional scans, we calculated pleiotropy likelihood ratio test statistics for each
pair of traits \citep{jiang1995multiple,boehm2019testing, boehm2019thesis}. Because of the required
computing time for bootstrap analyses, we didn't obtain p-values for the pleiotropy tests. Instead,
we worked directly with the test statistic values.
